---
title: "VPHi clinical Survey 2021 - Preprocessing script"
output: html_notebook
author: Raphaëlle Lesage
---

%Copyright (c) 2023 - Virtual Physiological Human institute (VPHi)

%Distributed under the GPLv3 License.
%     This program is free software: you can redistribute it and/or modify
%     it under the terms of the GNU General Public License as published by
%     the Free Software Foundation, either version 3 of the License, or
%     (at your option) any later version.
%     You should have received a copy of the GNU General Public License
%     along with this program.  If not, see <https://www.gnu.org/licenses/>



# Setup environment
```{r}
##set up chunk
# path management packages

# wrangling packages
library (here)
library(tidyverse) # for tidyr and dplyr
#library(data.table) #alternative to dplyr to work with table as sql
```

## Define path for storing results (here)
```{r}
here::i_am("2021_VPHi_clinical_survey_data.csv")
here = here::here()
output_folder = "Output"

if (!file.exists(here(here,output_folder))){
    dir.create(here(here,output_folder))
    print("Warning: folder was created")
} else {
    print("Warning: folder already exists")
    
}

```

# Pre-processing

## Load and clean data object
```{r}

f= here(here, "2021_VPHi_clinical_survey_data.csv")
rawdata = read.csv(f,header = TRUE)

medata_file = here(here, "Metadata.csv")
metadata = read.csv(medata_file,header = TRUE)


```

Clean Question 1: level of awareness

```{r}
questions = colnames(rawdata)
df= rawdata
categories = list("In.silico.medicine","Patient.specific.modelling","In.silico.clinical.trials","Virtual.Physiological.Human","Personalized.medicine","Digital.Twin")


for (c in 1:length(categories)){
  
  
  q_index = grep(categories[[c]],questions)
  temp = df[,q_index]!= ""
  Question = paste("Q1",categories[[c]],"awareness", sep=".")
  
  df[,Question] = as.character (df[,q_index[1]])
  
  for (i in 1:length(q_index)){
    q = q_index[i]
    rows = which(temp[,i])
    df[rows,Question] = as.character(df[rows,q])
  }
  
  df[,Question] = as.factor(df[,Question]) 
  
}

tdf = dplyr::tbl_df(df) # Convert to tibble  
tdf = tdf[,c(1:4,109:114,35:108)] #move Q1 back at the beginning and only keep aggregated version

# warning:Warning: `tbl_df()` was deprecated in dplyr 1.0.0. Please use `tibble::as_tibble()` instead.


```


Clean question 2: Technical background
```{r}

Biomed = tdf$Q2.Biomedical.Engineering != ""
tdf$Q2.Biomedical.Engineering = as.factor(Biomed)

tdf$Q2.Computer.Science = as.factor( tdf$Q2.Computer.Science != "")

tdf$Q2.Data.Science = as.factor(tdf$Q2.Data.Science != "")

tdf$Q2.Statistics = as.factor(tdf$Q2.Statistics != "")

tdf$Q2.Mathematics = as.factor(tdf$Q2.Mathematics != "")

tdf$Q2.Other = as.factor(tdf$Q2.Other != "")

#rename column for the case 'Other (please specify)';

colnames(tdf[16])="Q2.Other.technical.background"  #tdf %>%dplyr::rename(Other.technical.background = Other..please.specify.)

```

Clean question 4: method applied to practice
```{r}
tdf$Q4.Finite.Element.Analysis = as.factor( tdf$Q4.Finite.Element.Analysis != "")

tdf$Q4.Lumped.parameter.models = as.factor( tdf$Q4.Lumped.parameter.models!= "")

tdf$Q4.Computational.Fluid.Dynamics = as.factor( tdf$Q4.Computational.Fluid.Dynamics != "")

tdf$Q4.Fluid.structure.Interaction= as.factor( tdf$Q4.Fluid.structure.Interaction != "")

tdf$Q4.Multi.scale.1D.3D.modelling = as.factor( tdf$Q4.Multi.scale.1D.3D.modelling!= "")

tdf$Q4.Extended..e.g..Augmented..Virtual..Mixed..reality = as.factor( tdf$Q4.Extended..e.g..Augmented..Virtual..Mixed..reality != "")

tdf$Q4.Artificial.Interlligence.Machine.Learning = as.factor( tdf$Q4.Artificial.Interlligence.Machine.Learning != "")

tdf$Q4.Statistical.Shape.Modelling = as.factor( tdf$Q4.Statistical.Shape.Modelling != "")

tdf$Q4.None = as.factor( tdf$Q4.None != "")

tdf$Q4.Other.method.applied = as.factor( tdf$Q4.Other.method.applied != "")

```


Clean question 9: types of usage of CM&S
```{r}
tdf$Q9.Enrich.diagnosis= as.factor( tdf$Q9.Enrich.diagnosis != "")

tdf$Q9.Plan.interventions = as.factor( tdf$Q9.Plan.interventions!= "")

tdf$Q9.Compare.different.therapeutic.outcomes..retrospectively. = as.factor( tdf$Q9.Compare.different.therapeutic.outcomes..retrospectively. != "")

tdf$Q9.Teach= as.factor( tdf$Q9.Teach != "")

tdf$Q9.Study.Pathophysiology = as.factor( tdf$Q9.Study.Pathophysiology!= "")

tdf$Q9.Inform.the.patient.on.disease.progress = as.factor( tdf$Q9.Inform.the.patient.on.disease.progress != "")

tdf$Q9.Predict.compare.therapeutic.outcomes = as.factor( tdf$Q9.Predict.compare.therapeutic.outcomes != "")

tdf$Q9.None.of.the.above = as.factor( tdf$Q9.None.of.the.above != "")

tdf$Q9.Other.usage = as.factor( tdf$Q9.Other.usage != "")

```

Clean Q10 CM&S used for planning procedures (implement NA values for later stat analyses)
```{r}
tdf$Q10.use.for.planning[tdf$Q10.use.for.planning==""] = NA

```

Clean Q5 CM&S used for planning procedures
```{r}
tdf$Q5.Team.members.for.CMnS[tdf$Q5.Team.members.for.CMnS==""] = NA

```


Clean Q11: medical field of application
```{r}
q11 = grep("Q11",colnames(tdf))

temp = select(tdf, starts_with("Q11"))
temp2= dplyr::tbl_df(temp != "")

tdf[,q11] = temp2

```

Clean Q14: Trust scale (there should not be score= 0, but I found 3 of them.. replace by NA)
```{r}
which(tdf$Q14.Trust.scale==0)
tdf$Q14.Trust.scale[which(tdf$Q14.Trust.scale==0)]=NA
```


Clean Q15: Type of evidence for trusting CM&S
```{r}
q15 = grep("Q15",colnames(tdf))

temp = select(tdf, starts_with("Q15"))
temp2= dplyr::tbl_df(temp != "")

tdf[,q15] = temp2

```

Check class of variables
```{r}
sapply(tdf, class)
```


Convert categorical variables to ordinal: Q1, Q3, Q7, Q8, Q13 (Q14?--> continuous), Q19, (Q21: grant), 

```{r}

make_ordinal <- function(x,ordered_levels,exclude){
  if (exclude == TRUE){
    factor(x,order = TRUE, levels= ordered_levels, exclude = "")
  }  
  
  else {
    factor(x,order = TRUE, levels= ordered_levels)
  }
}

# Q1
  Awareness_levels= c('Not at all aware','Slightly aware','Moderately aware','Very aware','Extremely aware')
  Q1_ordinal = grep("Q1\\.",colnames(tdf))
  tdf[,Q1_ordinal] = lapply(tdf[,Q1_ordinal],make_ordinal, Awareness_levels,TRUE)
  sapply(tdf[,Q1_ordinal], class) #quality check

# Q3
  Familiarity_levels= c('','Not at all familiar','Slightly familiar','Moderately familiar','Very familiar','Extremely familiar')
  #colnames(tdf)[grep("Q3\\.",colnames(tdf))]
  Q3_ordinal= grep("Q3\\.",colnames(tdf))
  tdf[,Q3_ordinal] = lapply(tdf[,Q3_ordinal],make_ordinal, Familiarity_levels,TRUE)
  sapply(tdf[,Q3_ordinal], class)  #quality check

#Q7
  Q7_levels= c('','Definitely not','Probably not','Not sure','Probably yes','Definitely yes')
  Q_ordinal = grep("Q7\\.",colnames(tdf))
  tdf[,Q_ordinal] = lapply(tdf[,Q_ordinal],make_ordinal, Q7_levels,TRUE)
  sapply(tdf[,Q_ordinal], class) #quality check

#Q8
  Agreement_levels= c('','Strongly disagree','Disagree','Neutral','Agree','Strongly agree')
  Q_ordinal = grep("Q8\\.",colnames(tdf))
  tdf[,Q_ordinal] = lapply(tdf[,Q_ordinal],make_ordinal, Agreement_levels, TRUE)
  sapply(tdf[,Q_ordinal], class) #quality check

#Q13
  Frequency_levels= c('','Less than 5','5-10 times','11-20 times','>20 times')
  Q_ordinal = grep("Q13\\.",colnames(tdf))
  tdf[,Q_ordinal] = lapply(tdf[,Q_ordinal],make_ordinal, Frequency_levels, TRUE)
  sapply(tdf[,Q_ordinal], class) #quality check

```


## Saving Data:

```{r}
outfile_name <- "Preprocessed_data.Rds"
save_file_path <- here(output_folder, outfile_name)
saveRDS(object = tdf, file = save_file_path)

saveRDS(object = rawdata, file = here(output_folder, "Raw_data.Rds"))

```
