---
title: "Analysis of 2021 VPHi clinical Survey data"
output: html_notebook
author: Raphaëlle Lesage
---

%Copyright (c) 2023 - Virtual Physiological Human institute (VPHi)

%Distributed under the GPLv3 License.
%     This program is free software: you can redistribute it and/or modify
%     it under the terms of the GNU General Public License as published by
%     the Free Software Foundation, either version 3 of the License, or
%     (at your option) any later version.
%     You should have received a copy of the GNU General Public License
%     along with this program.  If not, see <https://www.gnu.org/licenses/>




# Setup environment
## Load librabries
```{r}
##set up chunk
# path management packages

# wrangling packages
library (here)
library(tidyverse) # for tidyr and dplyr
#library(data.table) #alternative to dplyr to work with table as sql

# analysis packages
library(coin) #for ordinal data analysis (Agresti, 2007)
library('DescTools')

# plotting packages
library(ggplot2) # ggplot environment
library(ggpubr) # publication ready plots
library(viridis) #color palet (yellow to blue)
library(corrplot)
library("gplots") #for balloonplot


```

## Define path for storing results (here)
```{r}
outfile_name <- "Preprocessed_data.Rds"
here::i_am("2021_VPHi_clinical_survey_data.csv")
here = here::here()
output_folder = "Output"
```

## Load pre-processed data
```{r}

save_file_path <- here(output_folder, outfile_name)
tdf <- readRDS(save_file_path)
rawdata <- readRDS(here(here,output_folder,"Raw_data.Rds"))


```

# Analysis


Define Likert scales' levels
```{r}
Awareness_levels= c('Not at all aware','Slightly aware','Moderately aware','Very aware','Extremely aware')
#Familiarity_levels= c('','Not at all familiar','Slightly familiar','Moderately familiar','Very familiar','Extremely familiar')
#Agreement_levels= c('','Strongly disagree','Disagree','Neutral','Agree','Strongly agree')

```

Get an overview of the data content and structure:
```{r}
#glimpse(tdf)
```


## Awareness and familiarity

Level of awareness in in silico concepts and terms: 
```{r}
summary(tdf[,5:10])

# print("Patient.specific.modelling.awareness :")
# table(tdf$Q1.Patient.specific.modelling.awareness)
# p1= prop.table(table(tdf$Q1.Patient.specific.modelling.awareness))*100

```
Visualize data:
```{r}
p1= prop.table(table(tdf$Q1.Patient.specific.modelling.awareness))*100
p2= prop.table(table(tdf$Q1.In.silico.clinical.trials.awareness))*100
p3= prop.table(table(tdf$Q1.Virtual.Physiological.Human.awareness))*100
p4= prop.table(table(tdf$Q1.Personalized.medicine.awareness))*100
p5= prop.table(table(tdf$Q1.Digital.Twin.awareness))*100


## plot histograms
par(mfrow=c(3,2))
  b1 = barplot(p1, main = "Patient specific modelling")
  text(x = b1, y = p1, label = round(p1,1), pos = 1, cex = 1, col = "red")
  
  b2 = barplot(p2, main = "In silico clinical trials")
  text(x = b2, y = p2, label = round(p2,1), pos = 1, cex = 1, col = "red")
  
  b3 = barplot(p3, main = "Virtual Physiological Human")
  text(x = b3, y = p3, label = round(p3,1), pos = 1, cex = 1, col = "red")
  
  b4 = barplot(p4, main = "Personalized medicine")
  text(x = b4, y = p4, label = round(p4,1), pos = 1, cex = 1, col = "red")
  
  b5 = barplot(p5, main = "Digital Twin")
  text(x = b5, y = p5, label = round(p5,1), pos = 1, cex = 1, col = "red")
```


Total number of answers (not NA) per question:
```{r}

cat("In.silico.medicine.awareness:", sum(table(tdf$Q1.In.silico.medicine.awareness)),"\n")
cat("Patient.specific.modelling.awareness:", sum(table(tdf$Q1.Patient.specific.modelling.awareness)),"\n")
cat("In.silico.clinical.trials.awareness:", sum(table(tdf$Q1.In.silico.clinical.trials.awareness)),"\n")
cat("Virtual.Physiological.Human.awareness: ", sum(table(tdf$Q1.Virtual.Physiological.Human.awareness)),"\n")
cat("Personalized.medicine.awareness:", sum(table(tdf$Q1.Personalized.medicine.awareness)),"\n")
cat("Digital.Twin.awareness:", sum(table(tdf$Q1.Digital.Twin.awareness)),"\n")

```



## level of familiarity with in silico methods

```{r}
summary(tdf[,17:24])
```

Total number of answers (not NA) per question:
```{r}
for (i in c(17:24)){
  cat(colnames(tdf[,i]),": ", sum(table(tdf[,i])), "\n")
}

```
## Technical background

Q2  is about CM&S related backgrounds represented in respondents' teams.
Data selection:
```{r}
tdf_Q2= select(tdf, starts_with("Q2."))

Q2_TRUE = lapply(tdf_Q2, as.logical) %>% lapply(which) %>% lapply(length) %>% as.data.frame() 
rownames(Q2_TRUE) =c("number_votes")

```

Visualize the responses for the 'Other' option of Q2 & correct data
```{r}
rawdata$Q2.Other[rawdata$Q2.Other != ""]

# 13 replies were identified as invalid (non CM&S related background)
Q2_TRUE$Q2.Other = Q2_TRUE$Q2.Other - 13
```

Number of votes by category
```{r}
as.data.frame(t(Q2_TRUE)) %>% arrange(desc(number_votes))
```


Visualize data with pie chart
```{r}
Q2 = cbind(summary(tdf$Q2.Biomedical.Engineering), summary(tdf$Q2.Computer.Science), summary(tdf$Q2.Data.Science), summary(tdf$Q2.Statistics), summary(tdf$Q2.Mathematics), summary(tdf$Q2.Other))
colnames(Q2)=colnames(tdf[,c(11:16)])

#Arrange Q2: the "Other" answers (free entry)  were manually grouped into CM&S related background and non-related background.
# The counts corresponding to non CM&S related entries are changed as 'FALSE' answers because we want to evaluate the total amount of CM&S related backgrounds only.

nonTech = Q2["TRUE","Q2.Other"]-13
Q2["FALSE","Q2.Other"]=Q2["FALSE","Q2.Other"]+nonTech
Q2["TRUE","Q2.Other"] = 13


pie(as.vector(Q2["TRUE",]), colnames(Q2), main= "Technical background")
```

How many individual respondents did not answer the question about technical background ?
```{r}
length(tdf$Respondent.ID[(tdf$Q2.Biomedical.Engineering ==FALSE)& (tdf$Q2.Computer.Science==FALSE) & (tdf$Q2.Data.Science==FALSE) & ( tdf$Q2.Statistics==FALSE) & (tdf$Q2.Mathematics ==FALSE) & (tdf$Q2.Other==FALSE)])
```
Team members dedicated to CM&S:
```{r}
tbl = table(tdf$Q5.Team.members.for.CMnS)
cbind(tbl,round(prop.table(tbl)*100,2))
```
## Usage and fequencies


Frequency of use fro planning intervention:
```{r}
barplot(prop.table(summary(tdf$Q13.how.often, na.omit=TRUE))*100, xlab= "Frequency of procedure planned with CM&S", ylab = "Percentage of votes")
```



What medical applications has CM&S been used for? :

```{r}

tdf_Q9= select(tdf, starts_with("Q9."))

Q9_TRUE = lapply(tdf_Q9, as.logical) %>% lapply(which) %>% lapply(length) %>% as.data.frame() 
rownames(Q9_TRUE) =c("number_votes")

as.data.frame(t(Q9_TRUE)) %>% arrange(desc(number_votes))


```

CM&S method applied to clinical practice

```{r}

tdf_Q4= select(tdf, starts_with("Q4."))

Q4_TRUE = lapply(tdf_Q4, as.logical) %>% lapply(which) %>% lapply(length) %>% as.data.frame() 
rownames(Q4_TRUE) =c("number_votes")

as.data.frame(t(Q4_TRUE)) %>% arrange(desc(number_votes))
```

## Association between medical specialty (Q11) and methods used by clinicians (Q4)


```{r}
medical_fields = as.list(colnames(tdf)[grep("Q11.",colnames(tdf))])
cms_methods = as.list(colnames(tdf)[grep("Q4.",colnames(tdf))])

Chi_pvalues=matrix(,nrow=length(medical_fields),ncol= length(cms_methods))
rownames(Chi_pvalues) =  list("Cardiovascular","Muskoskeletal","Cancer","Neuro degenerative","NA","Other") #medical_fields
colnames(Chi_pvalues) = list("Finite Element Analysis","Lumped parameter models","Computational Fluid Dynamics","Fluid structure Interaction", "Multiscale 1D/3D modelling","Extended,Virtual reality", "AI, ML","Statistical Shape Modelling","None", "Other method applied") #cms_methods


fish_pvalues=Chi_pvalues


for (m in 1:length(medical_fields)){
  for (c in 1:length(cms_methods)){
    med_field= medical_fields[[m]] # (otherwise use index with grep)
    cms_method= cms_methods[[c]]
    #tab = table(tdf[,med_field],tdf[,cms_method])
    tab = table(select(tdf,all_of(med_field), all_of(cms_method)))
    tab
    #print(list(med_field,cms_method))
    suppressWarnings(chisq <- chisq.test(tab))
    fish <- fisher.test(tab)
    # if (chisq$p.value < 0.05){
    #       corrplot(chisq$residuals, is.cor = FALSE, title=paste(med_field,cms_method), tl.pos=TRUE, method = "number")
    #   par(mar=c(5, 4, 4, 2) + 0.2)
    # }
    Chi_pvalues[m,c] = chisq$p.value
    fish_pvalues[m,c] = fish$p.value
  }
}


#Chi-test of association
corrplot(Chi_pvalues, is.cor = FALSE, method = "color",p.mat= Chi_pvalues, sig.level = c(0.001, 0.01, 0.05), insig = 'label_sig',pch.cex = 0.9)

#Fisher of association
corrplot(fish_pvalues, is.cor = FALSE, method = "color",p.mat= fish_pvalues, sig.level = c(0.001, 0.01, 0.05), insig = 'label_sig',pch.cex = 1,tl.col="black", cl.cex= 1, tl.cex=1.5, tl.srt=45)
```



## level of trust & awareness in technologies

### Check for trust distribution

```{r}
hist(tdf$Q14.Trust.scale, xlab = "Trust scale", cex.axis=1.5, cex.lab=1.5, main=NA)
m=round(mean(tdf$Q14.Trust.scale, na.rm= TRUE),2)
abline(v= m, col="red", lwd= 3)
text(x=m*1.35, y= 25, paste("Mean =", m),col="red",cex =1.2)
```

```{r}

cat("mean: ", mean(tdf$Q14.Trust.scale, na.rm= TRUE),"\n")
cat("standard deviation: ",sd(tdf$Q14.Trust.scale, na.rm = TRUE),"\n")
cat("number of answers (n): ", length((which(!is.na(tdf$Q14.Trust.scale)))),"\n")

```


### Check for trust distribution within level of awareness in in silico medicine (probability distribution per level of awareness):

```{r}
tab2 = table(select(tdf,Q1.Personalized.medicine.awareness, Q14.Trust.scale))
#gplots::balloonplot(tab2, main ="Q1.In.silico.medicine.awareness", xlab ="", ylab="", label = FALSE, show.margins = FALSE)


table(select(tdf,Q1.In.silico.medicine.awareness, Q14.Trust.scale))
```

Relation between trust and in silico medicine awareness:
```{r}
tab2 = table(select(tdf,Q1.In.silico.medicine.awareness, Q14.Trust.scale))

distrib = list()
distribution = vector()
countlength = vector()

# Histograms and density lines
par(mfrow=c(3, 2))
colnames <- dimnames(tab2)[[1]]
for (i in 1:5) {
  temp = vector()
  for (j in 1:10){
    temp= append(temp,rep(j,tab2[i,j]))
  }
  
  hist(temp,xlim = c(0,10), main=colnames[i], probability=TRUE, col="gray", border="white")
  d <- density(temp)
  lines(d, col="red")
  
  
  countlength = append(countlength, length(temp))
  distrib= append(distrib,list(temp))
  distribution= append(distribution,temp)
  
}


dat <- data.frame(dens = distribution
                  , lines = factor( rep( dimnames(tab2)[[1]], countlength ),levels=levels(tdf$Q1.In.silico.medicine.awareness)))

#Plot.
legend= "In silico medicine awareness"
ggplot(dat, aes(x = dens, fill = lines)) + geom_density(alpha = 0.5) + theme_classic()  + theme(axis.title = element_text(size=14), axis.text = element_text(size=14), legend.text= element_text(size=14), legend.title = element_text(size=12)) + labs(x="Trust", y="Desnity") + scale_fill_brewer(palette = "Spectral", direction = -1, name= legend)

```


### Difference of trust between user groups:

Define Users and non-Users group (based on Q4): create new variable, data$CMnS.Usage
```{r}

No_answers = (tdf$Q4.Finite.Element.Analysis==FALSE & tdf$Q4.Lumped.parameter.models==FALSE & tdf$Q4.Computational.Fluid.Dynamics==FALSE & tdf$Q4.Fluid.structure.Interaction==FALSE & tdf$Q4.Multi.scale.1D.3D.modelling == FALSE & tdf$Q4.Extended..e.g..Augmented..Virtual..Mixed..reality==FALSE & tdf$Q4.Artificial.Interlligence.Machine.Learning==FALSE & tdf$Q4.Statistical.Shape.Modelling==FALSE & tdf$Q4.Other.method.applied==FALSE & tdf$Q4.None==FALSE)

# # display ID of those observations that do not contain any answers:
# which(No_answers)

data = filter(tdf, !No_answers)

##
data = dplyr::mutate(data, CMnS.Usage = "Users")
data$CMnS.Usage[data$Q4.None==FALSE]="Non-Users"
data$CMnS.Usage = as.factor(data$CMnS.Usage)

```

### Q14 (trust) and Q4 (usage)
Is there a difference of trust between those who have even applied CM&S to their practive and those who haven't. 
```{r}

tab_Q4Q14 = table(dplyr::select(data, CMnS.Usage, Q14.Trust.scale))
# tab_Q4Q14
# prop.table(tab_Q4Q14, margin = 1)*100
# prop.table(tab_Q4Q14, margin = 2)*100
gplots::balloonplot(t(tab_Q4Q14), main = "",ylab = "Use of CM&S",label = TRUE, show.margins = FALSE, text.size=1.2)

boxplot(data$Q14.Trust.scale~ data$CMnS.Usage, ylab= "Q14.Trust.Scale", xlab= "CM&S usage")

# Violin plot basic
p <- ggplot(data, aes(x= CMnS.Usage, y= Q14.Trust.scale, color=CMnS.Usage)) + 
  geom_violin(trim=TRUE, size =1)  + stat_compare_means(method = "wilcox.test",label.y= 10.1, label.x = 1.25, size =5)
p + geom_boxplot(width=0.1, size =1) + theme_light() + theme(axis.title= element_text(size=20), axis.text = element_text(size = 20), legend.title = element_blank(), legend.text = element_text(size=20)) + labs(x = "Usage of CM&S", y="Trust scale")


```



### Q8 (statement agreement) versus Q4 (users - non users) 

Statements:
1. Computer modelling and simulation provides me with more confidence in planning procedures
2. Patient-specific computer modelling and simulation is accurate enough for clinical application
3. I have access to high performance computing
4. It would be impossible to finance a position for an expert in computer modelling and simulation in my institute
5. Computer modelling and simulation allows me to perform procedure faster
6. Patient-specific computer modelling and simulation is slow
7. There is no need for expertise on computer modelling and simulation in my team
8. Results of computer modelling and simulation are easy to understand



1. Computer modelling and simulation provides me with more confidence in planning procedures")

```{r}
sum(table(tdf$Q8.Agree.statement.1)) #Total number of responses for the statement
round(tdf$Q8.Agree.statement.1 %>% summary() %>% prop.table()*100)
```


2. Patient-specific computer modelling and simulation is accurate enough for clinical application

```{r}
sum(table(tdf$Q8.Agree.statement.2)) #Total number of responses for the statement
round(tdf$Q8.Agree.statement.2 %>% summary() %>% prop.table()*100)
```

3. I have access to high performance computing

```{r}
sum(table(tdf$Q8.Agree.statement.3)) #Total number of responses for the statement
round(tdf$Q8.Agree.statement.3 %>% summary() %>% prop.table()*100) #percentages of votes
```
4. It would be impossible to finance a position for an expert in computer modelling and simulation in my institute
```{r}
sum(table(tdf$Q8.Agree.statement.4)) #Total number of responses for the statement
round(tdf$Q8.Agree.statement.4 %>% summary() %>% prop.table()*100)  #percentages of votes
```
5. Computer modelling and simulation allows me to perform procedure faster
```{r}
sum(table(tdf$Q8.Agree.statement.5)) #Total number of responses for the statement
round(tdf$Q8.Agree.statement.5 %>% summary() %>% prop.table()*100) #percentages of votes
```
6. Patient-specific computer modelling and simulation is slow
```{r}
sum(table(tdf$Q8.Agree.statement.6)) #Total number of responses for the statement
round(tdf$Q8.Agree.statement.6 %>% summary() %>% prop.table()*100) #percentages of votes
```
7. There is no need for expertise on computer modelling and simulation in my team
```{r}
sum(table(tdf$Q8.Agree.statement.7)) #Total number of responses for the statement
round(tdf$Q8.Agree.statement.7 %>% summary() %>% prop.table()*100) #percentages of votes
```
8. Results of computer modelling and simulation are easy to understand
```{r}
sum(table(tdf$Q8.Agree.statement.8)) #Total number of responses for the statement
round(tdf$Q8.Agree.statement.8 %>% summary() %>% prop.table()*100) #percentages of votes
```



#### Association between experience using CM&S & agreement with statement 1 (Patient-specific computer modelling and simulation is accurate enough for clinical application):

Visualize association:
```{r}
#data is generated 
tab = table(dplyr::select(data, CMnS.Usage, Q8.Agree.statement.1))
#gplots::balloonplot(t(tab), main = "",ylab = "Use of CM&S",label = TRUE, show.margins = FALSE, text.size=1.2)


ggplot(data=subset(data,!is.na(Q8.Agree.statement.1)), aes(x=CMnS.Usage, y=Q8.Agree.statement.1, color = CMnS.Usage, na.rm= TRUE)) +
  geom_count() +
  annotate(geom ="text", label="Cochran-Armitage p-val=0.007", x=1.5,y=5.4 , size =1.5) +
  theme_light() +
  labs(x="Usage of CM&S", y="CM&S provides me with more confidence \n in planning procedures") +
  theme(axis.title = element_text(size=9), axis.text = element_text(size=9),legend.title = element_text(size=9)) +
  scale_color_manual(values = c("Non-Users" = "darkgrey", "Users" = "darkorange"))
#+ theme(aspect.ratio = 3/1)

#ggsave("plot_1.png", width = 3.5, height = 2.5)


```

Some statistics: Cochran-Armitage test is for cases where one variable is binary and one ordinal: usually, the binary variable is the response variable and the ordinal one is the explanatory variable.

Statistical tests:
```{r}
# statement 1: Patient-specific computer modelling and simulation is accurate enough for clinical application
#Agreement_levels= c('','Strongly disagree','Disagree','Neutral','Agree','Strongly agree')

tab_ca= data %>% dplyr::select(CMnS.Usage, Q8.Agree.statement.2) %>% table()
CochranArmitageTest(t(tab_ca))

coin::lbl_test(data %>% dplyr::select(CMnS.Usage, Q8.Agree.statement.1) %>% table() %>% t())

```


#### Association between experience using CM&S & other statements:
Visualize association for other statements:
```{r}
barplot(table(dplyr::select(data, CMnS.Usage, Q8.Agree.statement.1)), beside = TRUE, legend.text = TRUE, ylab= "number of respondents", xlab = "CM&S provides me with more confidence for planning procedures")

barplot(table(dplyr::select(data, CMnS.Usage, Q8.Agree.statement.2)), beside = TRUE, legend.text = TRUE, ylab= "number of respondents", xlab = "Patient specific modeling is accurate enough for clinical applications")
text(4,40,labels="Cochran-Armitage p-value = 0.007")

barplot(table(dplyr::select(data, CMnS.Usage, Q8.Agree.statement.3)), beside = TRUE, legend.text = TRUE, ylab= "number of respondents", xlab = "Patient specific modeling is slow")

barplot(table(dplyr::select(data, CMnS.Usage, Q8.Agree.statement.8)), beside = TRUE, legend.text = TRUE, ylab= "number of respondents", xlab = "CM&S allows me to perform procedure faster")


barplot(table(dplyr::select(data, CMnS.Usage, Q8.Agree.statement.6)), beside = TRUE, legend.text = TRUE, ylab= "number of respondents", xlab = "Results of computer modelling and simulation are easy to understand")


```


Statistics for association for other statements:
```{r}

CochranArmitageTest(data %>% dplyr::select(CMnS.Usage, Q8.Agree.statement.1) %>% table() %>% t())
CochranArmitageTest(data %>% dplyr::select(CMnS.Usage, Q8.Agree.statement.3) %>% table() %>% t())
CochranArmitageTest(data %>% dplyr::select(CMnS.Usage, Q8.Agree.statement.4) %>% table() %>% t())
CochranArmitageTest(data %>% dplyr::select(CMnS.Usage, Q8.Agree.statement.5) %>% table() %>% t())
CochranArmitageTest(data %>% dplyr::select(CMnS.Usage, Q8.Agree.statement.6) %>% table() %>% t())
CochranArmitageTest(data %>% dplyr::select(CMnS.Usage, Q8.Agree.statement.7) %>% table() %>% t())
CochranArmitageTest(data %>% dplyr::select(CMnS.Usage, Q8.Agree.statement.8) %>% table() %>% t())

# # Alternative more elegant code, but less reader friendly output
# index=grep("Q8\\.",colnames(data))
# 
# for (i in index){
#   data %>% dplyr::select(CMnS.Usage, all_of(i)) %>% table() %>% t() %>% CochranArmitageTest() %>% print()
# 
# }

```
### Role for expertise in the next 5 years
```{r}
barplot(prop.table(summary(tdf$Q7.role.for.CMnS.in.clinics, na.omit=TRUE))*100, xlab= "Frequency of procedure planned with CM&S", ylab = "Percentage of votes")
```


### Relation between team members dedicated to CM&S and use of CM&S for planning intervention (Q5 & Q10)

Visualize the contingency table (2 categorical variables):
```{r}

tab1 = table(tdf$Q5.Team.members.for.CMnS, tdf$Q10.use.for.planning)

xlabel = "Team members for CM&S"
ylabel= "Have used CM&S for planning interventions"

check_relation <- function(tab,colorscale,xlabel,ylabel){
  prop.table(tab1)*100 #percentages
  r= rowSums(tab)
  c = colSums(tab)
  s = spineplot(tab,  col=c("darkorange","darkgrey"), xlab=xlabel, ylab=ylabel) #col=viridis (colorscale)
  return(list(r=r,c=c,plot=s))
}


color_number= 2#3
l = check_relation(tab1,color_number,xlabel,ylabel)

# l$r
# l$c
l$plot
#prop.table(tab1, margin=1)*100

#Check if variables are independant (Chi-squared test) nominal variables:
chisq.test(tdf$Q5.Team.members.for.CMnS,tdf$Q10.use.for.planning)


```
### Required evidence to trust CM&S output
```{r}

tdf_Q15= select(tdf, starts_with("Q15."))

Q15_TRUE = lapply(tdf_Q15, as.logical) %>% lapply(which) %>% lapply(length) %>% as.data.frame() 
rownames(Q15_TRUE) =c("number_votes")

as.data.frame(t(Q15_TRUE)) %>% arrange(desc(number_votes))


filter(rawdata, Q15.Other.evidence != "") %>% select(starts_with("Q15.Other.evidence"))

```
# Supplementary Figures 

### Level of trust by level or awareness for all in silico terms

```{r}

#insilico_terms= colnames(select(tdf, starts_with("Q1.")))
insilico_terms_index = grep("Q1\\.",colnames(tdf))

for (c in insilico_terms_index){

  tab2 = table(select(tdf,all_of(c), Q14.Trust.scale))
  
  distrib = list()
  distribution = vector()
  countlength = vector()
  
  # Histograms and density lines
  par(mfrow=c(3, 2))
  colnames <- dimnames(tab2)[[1]]
  for (i in 1:5) {
    temp = vector()
    for (j in 1:10){
      temp= append(temp,rep(j,tab2[i,j]))
    }
    
    hist(temp,xlim = c(0,10), main=colnames[i], probability=TRUE, col="gray", border="white")
    d <- density(temp)
    lines(d, col="red")
    
    
    countlength = append(countlength, length(temp))
    distrib= append(distrib,list(temp))
    distribution= append(distribution,temp)
    
  }
  
  
  dat <- data.frame(dens = distribution
                    , lines = factor( rep( dimnames(tab2)[[1]], countlength ),levels=Awareness_levels))
  
  #Plot.
  legend= colnames(tdf[,all_of(c)])
  
  
  g = ggplot(dat, aes(x = dens, fill = lines)) + geom_density(alpha = 0.5) + theme_classic()  + theme(axis.title = element_text(size=14), axis.text = element_text(size=14), legend.text= element_text(size=14), legend.title = element_text(size=12)) + labs(x="Trust", y="Desnity") + scale_fill_brewer(palette = "Spectral", direction = -1, name= legend)
  
  print(g)
  #ggsave("Trust_by_awareness1.png", width = 7, height = 5)
  
}


```

### Association between Role for expertise envisionned & team members dedicated to CM&S

Visualize the contingency table (2 categorical variables):
```{r}


tab1 = table(tdf$Q7.role.for.CMnS.in.clinics, tdf$Q5.Team.members.for.CMnS)
dimnames(tab1)=list("Role"=rownames(tab1), "Team.members"= colnames(tab1))


color_number= 2#3
l = check_relation(tab1,color_number,"See a role for CM&S in clinics in next 5 years","Have team members dedicated to CM&S")

# l$r
# l$c
l$plot

#gplots::balloonplot(t(tab1), main ="Contingency table", xlab ="", ylab="", label = FALSE, show.margins = FALSE)


# statistical test:  Cochran and Armitage test for the particular case when y is a binary factor and x is ordered
coin::chisq_test(tab1, scores=list("Role"=c(-2,-1,0,1,2)))

  
  

```


